
```{r} 


library(ggplot2)
library(data.table)
library(patchwork)
library(dplyr)
library(tidyr)

#sets working DIR
setwd("")
datapath <- ""
```
##Violin Plots
#Poly(A) length in just FOXP3

```{r} 
###Violin plots
##violin plots of the Poly(A) in just FOXP3
#reads files and creates a dataframe
FOXP3reads1<- fread(paste0(datapath, "/13_Cases-Treg-5/reads.FOXP3.Poly-A.20240917_1258_MN32174_FAZ55036_ddd49ffc.txt"), col.names = c('count', 'Poly_A_length'))
FOXP3reads2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/reads.FOXP3.Poly-A.Cases-HD3-Treg-3.txt"), col.names = c('count', 'Poly_A_length'))
FOXP3reads3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/reads.FOXP3.Poly-A.Cases-HD3-Treg-6.txt"), col.names = c('count', 'Poly_A_length'))
FOXP3reads4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/reads.FOXP3.Poly-A.20211208_HD42_Lib1_dRNA002.txt"), col.names = c('count', 'Poly_A_length'))
FOXP3reads5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/reads.FOXP3.Poly-A.20211209_HD42_Lib1_RNA002.txt"), col.names = c('count', 'Poly_A_length'))
FOXP3reads6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/reads.FOXP3.Poly-A.20220105_HD43_dRNA_RNA002.txt"), col.names = c('count', 'Poly_A_length'))
FOXP3reads7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/reads.FOXP3.Poly-A.20240612_1358_MN32174_FAX88319_e12cfcb1.txt"), col.names = c('count', 'Poly_A_length'))
FOXP3reads8<- fread(paste0(datapath, "/12_Cases_Tconv-7/reads.FOXP3.Poly-A.20240911_1327_MN32174_FAZ54913_6b9afda9.txt"), col.names = c('count', 'Poly_A_length'))


#sets read ID-Column to Name of data set
FOXP3reads1$sample<-"Cases-Treg-5"
FOXP3reads2$sample<-"Cases-HD3-Treg-3"
FOXP3reads3$sample<-"Cases-HD3-Treg-6"
FOXP3reads4$sample<-"20211208_HD42_Lib1_dRNA002"
FOXP3reads5$sample<-"20211209_HD42_Lib1_RNA002"
FOXP3reads6$sample<-"20220105_HD43_dRNA_RNA002"
FOXP3reads7$sample<-"Cases-Treg-HD2"
FOXP3reads8$sample<-"Cases_Tconv-7"

#combine files to one 
FOXP3_length <- rbind(FOXP3reads1,FOXP3reads2,FOXP3reads3,FOXP3reads4,FOXP3reads5,FOXP3reads6,FOXP3reads7,FOXP3reads8)
  #removes unused data, to save RAM capacity
    rm(FOXP3reads1,FOXP3reads2,FOXP3reads3,FOXP3reads4,FOXP3reads5,FOXP3reads6,FOXP3reads7,FOXP3reads8)
#creates violin plots
FOXP3_v <- ggplot(FOXP3_length, aes(x=sample, y=Poly_A_length)) +
            geom_violin(scale = "width")  + 
            geom_boxplot(width=0.03, outlier.shape = NA) + 
            ggtitle ("Length of Poly(A)-Tails in FOPX3") + 
            theme_classic()+
            labs(x = NULL)+
            theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

#Poly(A) length in the whole genome

```{r} 
##violin plots of the Poly(A) in the whole sample
#reads files and creates a dataframe
Wholereads1<- fread(paste0(datapath, "/13_Cases-Treg-5/reads.Poly-A.20240917_1258_MN32174_FAZ55036_ddd49ffc.txt"), col.names = c('count', 'Poly_A_length'))
Wholereads2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/reads.Poly-A.Cases-HD3-Treg-3.txt"), col.names = c('count', 'Poly_A_length'))
Wholereads3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/reads.Poly-A.Cases-HD3-Treg-6.txt"), col.names = c('count', 'Poly_A_length'))
Wholereads4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/reads.Poly-A.20211208_HD42_Lib1_dRNA002.txt"), col.names = c('count', 'Poly_A_length'))
Wholereads5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/reads.Poly-A.20211209_HD42_Lib1_RNA002.txt"), col.names = c('count', 'Poly_A_length'))
Wholereads6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/reads.Poly-A.20220105_HD43_dRNA_RNA002.txt"), col.names = c('count', 'Poly_A_length'))
Wholereads7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/reads.Poly-A.20240612_1358_MN32174_FAX88319_e12cfcb1.txt"), col.names = c('count', 'Poly_A_length'))
Wholereads8<- fread(paste0(datapath, "/12_Cases_Tconv-7/reads.Poly-A.20240911_1327_MN32174_FAZ54913_6b9afda9.txt"), col.names = c('count', 'Poly_A_length'))

#sets read ID-Column to Name of data set
Wholereads1$sample<-"Cases-Treg-5"
Wholereads2$sample<-"Cases-HD3-Treg-3"
Wholereads3$sample<-"Cases-HD3-Treg-6"
Wholereads4$sample<-"20211208_HD42_Lib1_dRNA002"
Wholereads5$sample<-"20211209_HD42_Lib1_RNA002"
Wholereads6$sample<-"20220105_HD43_dRNA_RNA002"
Wholereads7$sample<-"Cases-Treg-HD2"
Wholereads8$sample<-"Cases_Tconv-7"

#combine files to one 
whole_length <- rbind(Wholereads1,Wholereads2,Wholereads3,Wholereads4,Wholereads5,Wholereads6,Wholereads7, Wholereads8)
     #removes unused data, to save RAM capacity
        rm(Wholereads1,Wholereads2,Wholereads3,Wholereads4,Wholereads5,Wholereads6,Wholereads7, Wholereads8)
#creates violin plots
whole_v <- ggplot(whole_length, aes(x=sample, y=Poly_A_length)) +
            geom_violin(scale = "width")  + 
            geom_boxplot(width=0.03,  outlier.shape = NA) +
            ggtitle ("Length of Poly(A)-Tails in whole genome") + 
            labs(x = NULL)+
            theme_classic() +
            theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


#Poly(A) length in the whole genome zoomed to foxp3
```{r}                   
#creates violin plots
whole_zoom_v <- ggplot(whole_length, aes(x=sample, y=Poly_A_length)) +
            geom_violin(scale = "width")  + 
            geom_boxplot(width=0.03,  outlier.shape = NA) +
            scale_y_continuous(limits = c(0, 400)) +
            ggtitle ("Length of Poly(A)-Tails in whole genome (zoomed)") +
            labs(x = NULL)+
            theme_classic()    +
            theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

##Boxplots
#Poly-A-detection in FOXP3

```{r} 
###Boxplots for proportion of Poly-A-Tails
##just FOXP3

#reads files and creates a dataframe
FOXP3counts1<- fread(paste0(datapath, "/13_Cases-Treg-5/counts.FOXP3.Poly-A.20240917_1258_MN32174_FAZ55036_ddd49ffc.txt"), col.names = c('count', 'reads'))
FOXP3counts2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/counts.FOXP3.Poly-A.Cases-HD3-Treg-3.txt"), col.names = c('count', 'reads'))
FOXP3counts3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/counts.FOXP3.Poly-A.Cases-HD3-Treg-6.txt"), col.names = c('count', 'reads'))
FOXP3counts4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/counts.FOXP3.Poly-A.20211208_HD42_Lib1_dRNA002.txt"), col.names = c('count', 'reads'))
FOXP3counts5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/counts.FOXP3.Poly-A.20211209_HD42_Lib1_RNA002.txt"), col.names = c('count', 'reads'))
FOXP3counts6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/counts.FOXP3.Poly-A.20220105_HD43_dRNA_RNA002.txt"), col.names = c('count', 'reads'))
FOXP3counts7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/counts.FOXP3.Poly-A.20240612_1358_MN32174_FAX88319_e12cfcb1.txt"), col.names = c('count', 'reads'))
FOXP3counts8<- fread(paste0(datapath, "/12_Cases_Tconv-7/counts.FOXP3.Poly-A.20240911_1327_MN32174_FAZ54913_6b9afda9.txt"), col.names = c('count', 'reads'))

#sets read ID-Column to Name of data set
FOXP3counts1$sample <- "Cases-Treg-5"; FOXP3counts1[1, 2] <- "no Poly(A)-Tail"; FOXP3counts1[2, 2] <- "Poly(A)-Tail detected"
FOXP3counts2$sample <- "Cases-HD3-Treg-3"; FOXP3counts2[1, 2] <- "no Poly(A)-Tail"; FOXP3counts2[2, 2] <- "Poly(A)-Tail detected"
FOXP3counts3$sample <- "Cases-HD3-Treg-6"; FOXP3counts3[1, 2] <- "no Poly(A)-Tail"; FOXP3counts3[2, 2] <- "Poly(A)-Tail detected"
FOXP3counts4$sample <- "20211208_HD42_Lib1_dRNA002"; FOXP3counts4[1, 2] <- "no Poly(A)-Tail"; FOXP3counts4[2, 2] <- "Poly(A)-Tail detected"
FOXP3counts5$sample <- "20211209_HD42_Lib1_RNA002"; FOXP3counts5[1, 2] <- "no Poly(A)-Tail"; FOXP3counts5[2, 2] <- "Poly(A)-Tail detected"
FOXP3counts6$sample <- "20220105_HD43_dRNA_RNA002"; FOXP3counts6[1, 2] <- "no Poly(A)-Tail"; FOXP3counts6[2, 2] <- "Poly(A)-Tail detected"
FOXP3counts7$sample <- "Cases-Treg-HD2"; FOXP3counts7[1, 2] <- "no Poly(A)-Tail"; FOXP3counts7[2, 2] <- "Poly(A)-Tail detected"
FOXP3counts8$sample <- "Cases_Tconv-7"; FOXP3counts8[1, 2] <- "no Poly(A)-Tail"; FOXP3counts8[2, 2] <- "Poly(A)-Tail detected"


#combine files to one 
count <- rbind(FOXP3counts1,FOXP3counts2,FOXP3counts3,FOXP3counts4,FOXP3counts5,FOXP3counts6,FOXP3counts7,FOXP3counts8 )

# Calculate the proportion for each type within each sample
#sample 1
count$count[2] <- FOXP3counts1$count[2]/FOXP3counts1$count[1]
count$count[1] <- 1-count$count[2]
count$count[4] <- FOXP3counts2$count[2]/FOXP3counts2$count[1]
count$count[3] <- 1-count$count[4]
count$count[6] <- FOXP3counts3$count[2]/FOXP3counts3$count[1]
count$count[5] <- 1-count$count[6]
count$count[8] <- FOXP3counts4$count[2]/FOXP3counts4$count[1]
count$count[7] <- 1-count$count[8]
count$count[10] <- FOXP3counts5$count[2]/FOXP3counts5$count[1]
count$count[9] <- 1-count$count[10]
count$count[12] <- FOXP3counts6$count[2]/FOXP3counts6$count[1]
count$count[11] <- 1-count$count[12]
count$count[14] <- FOXP3counts7$count[2]/FOXP3counts7$count[1]
count$count[13] <- 1-count$count[14]
count$count[16] <- FOXP3counts8$count[2]/FOXP3counts8$count[1]
count$count[15] <- 1-count$count[16]

  #removes unused data, to save RAM capacity
   rm(FOXP3counts1,FOXP3counts2,FOXP3counts3,FOXP3counts4,FOXP3counts5,FOXP3counts6,FOXP3counts7,FOXP3counts8)

FOXP3_counts <- ggplot(count, aes(fill=reads, y=count , x=sample)) + 
  geom_bar(stat = "identity") + 
  ggtitle ("Poly(A)-Tails in FOXP3") +
  labs(x = NULL)+
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

#Poly-A-detection in the whole genome
```{r} 
##whole Genome

#reads files and creates a dataframe
wholecounts1<- fread(paste0(datapath, "/13_Cases-Treg-5/counts.whole.Poly-A.20240917_1258_MN32174_FAZ55036_ddd49ffc.txt"), col.names = c('count', 'reads'))
wholecounts2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/counts.whole.Poly-A.Cases-HD3-Treg-3.txt"), col.names = c('count', 'reads'))
wholecounts3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/counts.whole.Poly-A.Cases-HD3-Treg-6.txt"), col.names = c('count', 'reads'))
wholecounts4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/counts.whole.Poly-A.20211208_HD42_Lib1_dRNA002.txt"), col.names = c('count', 'reads'))
wholecounts5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/counts.whole.Poly-A.20211209_HD42_Lib1_RNA002.txt"), col.names = c('count', 'reads'))
wholecounts6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/counts.whole.Poly-A.20220105_HD43_dRNA_RNA002.txt"), col.names = c('count', 'reads'))
wholecounts7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/counts.whole.Poly-A.20240612_1358_MN32174_FAX88319_e12cfcb1.txt"), col.names = c('count', 'reads'))
wholecounts8<- fread(paste0(datapath, "/12_Cases_Tconv-7/counts.whole.Poly-A.20240911_1327_MN32174_FAZ54913_6b9afda9.txt"), col.names = c('count', 'reads'))

#sets read ID-Column to Name of data set
wholecounts1$sample <- "Cases-Treg-5"; wholecounts1[1, 2] <- "no Poly(A)-Tail"; wholecounts1[2, 2] <- "Poly(A)-Tail detected"
wholecounts2$sample <- "Cases-HD3-Treg-3"; wholecounts2[1, 2] <- "no Poly(A)-Tail"; wholecounts2[2, 2] <- "Poly(A)-Tail detected"
wholecounts3$sample <- "Cases-HD3-Treg-6"; wholecounts3[1, 2] <- "no Poly(A)-Tail"; wholecounts3[2, 2] <- "Poly(A)-Tail detected"
wholecounts4$sample <- "20211208_HD42_Lib1_dRNA002"; wholecounts4[1, 2] <- "no Poly(A)-Tail"; wholecounts4[2, 2] <- "Poly(A)-Tail detected"
wholecounts5$sample <- "20211209_HD42_Lib1_RNA002"; wholecounts5[1, 2] <- "no Poly(A)-Tail"; wholecounts5[2, 2] <- "Poly(A)-Tail detected"
wholecounts6$sample <- "20220105_HD43_dRNA_RNA002"; wholecounts6[1, 2] <- "no Poly(A)-Tail"; wholecounts6[2, 2] <- "Poly(A)-Tail detected"
wholecounts7$sample <- "Cases-Treg-HD2"; wholecounts7[1, 2] <- "no Poly(A)-Tail"; wholecounts7[2, 2] <- "Poly(A)-Tail detected"
wholecounts8$sample <- "Cases_Tconv-7"; wholecounts8[1, 2] <- "no Poly(A)-Tail"; wholecounts8[2, 2] <- "Poly(A)-Tail detected"


#combine files to one 
whole_count <- rbind(wholecounts1,wholecounts2,wholecounts3,wholecounts4,wholecounts5,wholecounts6,wholecounts7, wholecounts8)


# Calculate the proportion for each type within each sample
#sample 1
whole_count$count[2] <- wholecounts1$count[2]/wholecounts1$count[1]
whole_count$count[1] <- 1-whole_count$count[2]
whole_count$count[4] <- wholecounts2$count[2]/wholecounts2$count[1]
whole_count$count[3] <- 1-whole_count$count[4]
whole_count$count[6] <- wholecounts3$count[2]/wholecounts3$count[1]
whole_count$count[5] <- 1-whole_count$count[6]
whole_count$count[8] <- wholecounts4$count[2]/wholecounts4$count[1]
whole_count$count[7] <- 1-whole_count$count[8]
whole_count$count[10] <- wholecounts5$count[2]/wholecounts5$count[1]
whole_count$count[9] <- 1-whole_count$count[10]
whole_count$count[12] <- wholecounts6$count[2]/wholecounts6$count[1]
whole_count$count[11] <- 1-whole_count$count[12]
whole_count$count[14] <- wholecounts7$count[2]/wholecounts7$count[1]
whole_count$count[13] <- 1-whole_count$count[14]
whole_count$count[16] <- wholecounts8$count[2]/wholecounts8$count[1]
whole_count$count[15] <- 1-whole_count$count[16]

  #removes unused data, to save RAM capacity
    rm(wholecounts1,wholecounts2,wholecounts3,wholecounts4,wholecounts5,wholecounts6,wholecounts7, wholecounts8)


whole_counts <- ggplot(whole_count, aes(fill=reads, y=count , x=sample)) + 
  geom_bar(stat = "identity")+
  ggtitle ("Poly(A)-Tails in whole genome") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = NULL)+
  #theme(axis.title.x=element_blank())
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

``` 
##Plot Creation of Poly-A Overview 
```{r} 
#creating a graph using patchwork
(FOXP3_v | whole_v | whole_zoom_v) /
(FOXP3_counts | whole_counts)

```

##Stacked Bar plots
#Composition of aligned reads
```{r} 
##  
#reads counts files of HG38 align
HG38_readcount1<- fread(paste0(datapath, "/13_Cases-Treg-5/readcount.totalHG38.alignment.txt"), col.names = c('count', 'readtype'))
HG38_readcount2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/readcount.totalHG38.alignment.txt"), col.names = c('count', 'readtype'))
HG38_readcount3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/readcount.totalHG38.alignment.txt"), col.names = c('count', 'readtype'))
HG38_readcount4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/readcount.totalHG38.alignment.txt"), col.names = c('count', 'readtype'))
HG38_readcount5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/readcount.totalHG38.alignment.txt"), col.names = c('count', 'readtype'))
HG38_readcount6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/readcount.totalHG38.alignment.txt"), col.names = c('count', 'readtype'))
HG38_readcount7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/readcount.totalHG38.alignment.txt"), col.names = c('count', 'readtype'))
HG38_readcount8<- fread(paste0(datapath, "/12_Cases_Tconv-7/readcount.totalHG38.alignment.txt"), col.names = c('count', 'readtype'))

  #changes values to appropriate type
  HG38_readcount1$readtype <- with(HG38_readcount1, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  HG38_readcount2$readtype <- with(HG38_readcount2, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  HG38_readcount3$readtype <- with(HG38_readcount3, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  HG38_readcount4$readtype <- with(HG38_readcount4, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  HG38_readcount5$readtype <- with(HG38_readcount5, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  HG38_readcount6$readtype <- with(HG38_readcount6, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  HG38_readcount7$readtype <- with(HG38_readcount7, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  HG38_readcount8$readtype <- with(HG38_readcount8, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  
  #add sampletype to data
  HG38_readcount1$sample <- "Cases-Treg-5"
  HG38_readcount1$type <- "HG38"
  HG38_readcount2$sample <- "Cases-HD3-Treg-3"
  HG38_readcount2$type <- "HG38"
  HG38_readcount3$sample <- "Cases-HD3-Treg-6"
  HG38_readcount3$type <- "HG38"
  HG38_readcount4$sample <- "20211208_HD42_Lib1_dRNA002"
  HG38_readcount4$type <- "HG38"
  HG38_readcount5$sample <- "20211209_HD42_Lib1_RNA002"
  HG38_readcount5$type <- "HG38"
  HG38_readcount6$sample <- "20220105_HD43_dRNA_RNA002"
  HG38_readcount6$type <- "HG38"
  HG38_readcount7$sample <- "Cases-Treg-HD2"
  HG38_readcount7$type <- "HG38"
  HG38_readcount8$sample <- "Cases_Tconv-7" 
  HG38_readcount8$type <- "HG38"

##reads counts files of HG38&ENO2 align
all_readcount1<- fread(paste0(datapath, "/13_Cases-Treg-5/readcount.totalHG38_ENO2.alignment.txt"), col.names = c('count', 'readtype'))
all_readcount2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/readcount.totalHG38_ENO2.alignment.txt"), col.names = c('count', 'readtype'))
all_readcount3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/readcount.totalHG38_ENO2.alignment.txt"), col.names = c('count', 'readtype'))
all_readcount4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/readcount.totalHG38_ENO2.alignment.txt"), col.names = c('count', 'readtype'))
all_readcount5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/readcount.totalHG38_ENO2.alignment.txt"), col.names = c('count', 'readtype'))
all_readcount6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/readcount.totalHG38_ENO2.alignment.txt"), col.names = c('count', 'readtype'))
all_readcount7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/readcount.totalHG38_ENO2.alignment.txt"), col.names = c('count', 'readtype'))
all_readcount8<- fread(paste0(datapath, "/12_Cases_Tconv-7/readcount.totalHG38_ENO2.alignment.txt"), col.names = c('count', 'readtype'))

  #changes values to appropriate type
  all_readcount1$readtype <- with(all_readcount1, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  all_readcount2$readtype <- with(all_readcount2, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  all_readcount3$readtype <- with(all_readcount3, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  all_readcount4$readtype <- with(all_readcount4, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  all_readcount5$readtype <- with(all_readcount5, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  all_readcount6$readtype <- with(all_readcount6, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  all_readcount7$readtype <- with(all_readcount7, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  all_readcount8$readtype <- with(all_readcount8, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))

  #add sampletype to data
  all_readcount1$sample <- "Cases-Treg-5"
  all_readcount1$type <- "all"
  all_readcount2$sample <- "Cases-HD3-Treg-3"
  all_readcount2$type <- "all"
  all_readcount3$sample <- "Cases-HD3-Treg-6"
  all_readcount3$type <- "all"
  all_readcount4$sample <- "20211208_HD42_Lib1_dRNA002"
  all_readcount4$type <- "all"
  all_readcount5$sample <- "20211209_HD42_Lib1_RNA002"
  all_readcount5$type <- "all"
  all_readcount6$sample <- "20220105_HD43_dRNA_RNA002"
  all_readcount6$type <- "all"
  all_readcount7$sample <- "Cases-Treg-HD2"
  all_readcount7$type <- "all"
  all_readcount8$sample <- "Cases_Tconv-7" 
  all_readcount8$type <- "all" 
 
##reads counts files of just ENO2 align
ENO2_readcount1<- fread(paste0(datapath, "/13_Cases-Treg-5/readcount.ENO2.alignment.txt"), col.names = c('count', 'readtype'))
ENO2_readcount2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/readcount.ENO2.alignment.txt"), col.names = c('count', 'readtype'))
ENO2_readcount3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/readcount.ENO2.alignment.txt"), col.names = c('count', 'readtype'))
ENO2_readcount4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/readcount.ENO2.alignment.txt"), col.names = c('count', 'readtype'))
ENO2_readcount5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/readcount.ENO2.alignment.txt"), col.names = c('count', 'readtype'))
ENO2_readcount6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/readcount.ENO2.alignment.txt"), col.names = c('count', 'readtype'))
ENO2_readcount7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/readcount.ENO2.alignment.txt"), col.names = c('count', 'readtype'))
ENO2_readcount8<- fread(paste0(datapath, "/12_Cases_Tconv-7/readcount.ENO2.alignment.txt"), col.names = c('count', 'readtype'))

  #changes values to appropriate type
  ENO2_readcount1$readtype <- with(ENO2_readcount1, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  ENO2_readcount2$readtype <- with(ENO2_readcount2, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  ENO2_readcount3$readtype <- with(ENO2_readcount3, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  ENO2_readcount4$readtype <- with(ENO2_readcount4, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  ENO2_readcount5$readtype <- with(ENO2_readcount5, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  ENO2_readcount6$readtype <- with(ENO2_readcount6, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  ENO2_readcount7$readtype <- with(ENO2_readcount7, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))
  ENO2_readcount8$readtype <- with(ENO2_readcount8, ifelse(readtype %in% c(0, 16), "aligned", 
                                    ifelse(readtype == 4, "non aligned",
                                        "supplemental")))

  #add sampletype to data
  ENO2_readcount1$sample <- "Cases-Treg-5"
  ENO2_readcount1$type <- "ENO2"
  ENO2_readcount2$sample <- "Cases-HD3-Treg-3"
  ENO2_readcount2$type <- "ENO2"
  ENO2_readcount3$sample <- "Cases-HD3-Treg-6"
  ENO2_readcount3$type <- "ENO2"
  ENO2_readcount4$sample <- "20211208_HD42_Lib1_dRNA002"
  ENO2_readcount4$type <- "ENO2"
  ENO2_readcount5$sample <- "20211209_HD42_Lib1_RNA002"
  ENO2_readcount5$type <- "ENO2"
  ENO2_readcount6$sample <- "20220105_HD43_dRNA_RNA002"
  ENO2_readcount6$type <- "ENO2"
  ENO2_readcount7$sample <- "Cases-Treg-HD2"
  ENO2_readcount7$type <- "ENO2"
  ENO2_readcount8$sample <- "Cases_Tconv-7" 
  ENO2_readcount8$type <- "ENO2"  

#combine all files into one for graph creation
readcomposition <- rbind(HG38_readcount1, all_readcount1, ENO2_readcount1,
                         HG38_readcount2, all_readcount2, ENO2_readcount2,
                         HG38_readcount3, all_readcount3, ENO2_readcount3,
                         HG38_readcount4, all_readcount4, ENO2_readcount4,
                         HG38_readcount5, all_readcount5, ENO2_readcount5,
                         HG38_readcount6, all_readcount6, ENO2_readcount6,
                         HG38_readcount7, all_readcount7, ENO2_readcount7,
                         HG38_readcount8, all_readcount8, ENO2_readcount8)
  #removes unused data, to save RAM capacity
          rm(HG38_readcount1, all_readcount1, ENO2_readcount1,
                         HG38_readcount2, all_readcount2, ENO2_readcount2,
                         HG38_readcount3, all_readcount3, ENO2_readcount3,
                         HG38_readcount4, all_readcount4, ENO2_readcount4,
                         HG38_readcount5, all_readcount5, ENO2_readcount5,
                         HG38_readcount6, all_readcount6, ENO2_readcount6,
                         HG38_readcount7, all_readcount7, ENO2_readcount7,
                         HG38_readcount8, all_readcount8, ENO2_readcount8)
          
# Filter the data according to your conditions
readcomposition_filtered <- readcomposition[(readcomposition$readtype == "aligned" & readcomposition$type == "HG38") | 
                                            (readcomposition$readtype == "non aligned" & readcomposition$type == "all") | 
                                            (readcomposition$readtype == "aligned" & readcomposition$type == "ENO2"),]

# Sum the count for each group 
readcomposition_summary <- aggregate(count ~ sample+readtype+type, readcomposition_filtered, sum )

# Creates legend for plot
readcomposition_summary$legend <- readcomposition_summary$type
readcomposition_summary$legend[readcomposition_summary$readtype == "non aligned"] <- "non aligned"

#Calculate the proportion for each group
readcomposition_summary <- within(readcomposition_summary, {
  prop <- ave(count, sample, FUN=function(x) x/sum(x)*100)
})

#creates stacked bar plot
readcomposition_bp <- ggplot(readcomposition_summary, aes(x=sample, y=prop, fill=legend)) +
  geom_bar(stat="identity", position="stack") +
  xlab("Sample") +
  ylab("Percentage") +
  labs(x = NULL)+
  ggtitle("Genome alignment of reads") +
  scale_y_continuous(labels = function(y) paste0(y, "%")) +
  geom_text(aes(label=paste0(round(prop,1),"%")), position=position_stack(vjust=0.5)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


``` 

##Plot Creation of alignment overview
```{r} 

(readcomposition_bp)

``` 

##Violin Plots
#Read length distribution 
#all aligning reads 
```{r} 
#reads files and creates a dataframe
all_readslength1<- fread(paste0(datapath, "/13_Cases-Treg-5/readlength.all.aligning.txt"), col.names = c('readlength'))
all_readslength2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/readlength.all.aligning.txt"), col.names = c('readlength'))
all_readslength3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/readlength.all.aligning.txt"), col.names = c('readlength'))
all_readslength4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/readlength.all.aligning.txt"), col.names = c('readlength'))
all_readslength5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/readlength.all.aligning.txt"), col.names = c('readlength'))
all_readslength6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/readlength.all.aligning.txt"), col.names = c('readlength'))
all_readslength7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/readlength.all.aligning.txt"), col.names = c('readlength'))
all_readslength8<- fread(paste0(datapath, "/12_Cases_Tconv-7/readlength.all.aligning.txt"), col.names = c('readlength'))


#sets read ID-Column to Name of data set
all_readslength1$sample<-"Cases-Treg-5"
all_readslength2$sample<-"Cases-HD3-Treg-3"
all_readslength3$sample<-"Cases-HD3-Treg-6"
all_readslength4$sample<-"20211208_HD42_Lib1_dRNA002"
all_readslength5$sample<-"20211209_HD42_Lib1_RNA002"
all_readslength6$sample<-"20220105_HD43_dRNA_RNA002"
all_readslength7$sample<-"Cases-Treg-HD2"
all_readslength8$sample<-"Cases_Tconv-7"

#combine files to one 
whole_allreadslength <- rbind(all_readslength1,all_readslength2,all_readslength3,all_readslength4,all_readslength5,all_readslength6,all_readslength7,all_readslength8)
   #removes unused data, to save RAM capacity
          rm(all_readslength1,all_readslength2,all_readslength3,all_readslength4,all_readslength5,all_readslength6,all_readslength7,all_readslength8)
          
#creates violin plots
all_readslength_v <- ggplot(whole_allreadslength, 
                  aes(x=sample, y=readlength)) + 
                  geom_violin(scale = "width")  + 
                  geom_boxplot(width=0.03,  outlier.shape = NA) + 
                  labs(x = NULL)+
                  scale_y_continuous(limits = c(0, 5000)) +
                  ggtitle ("Length of all aligning reads") + 
                  theme_classic() + 
                  theme(axis.text.x = element_text(angle = 45, hjust = 1))
``` 

#Read length distribution 
#all reads after basecalling
```{r} 
#reads files and creates a dataframe
dorado_readslength1<- fread(paste0(datapath, "/13_Cases-Treg-5/readlength.dorado.txt"), col.names = c('readlength'))
dorado_readslength2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/readlength.dorado.txt"), col.names = c('readlength'))
dorado_readslength3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/readlength.dorado.txt"), col.names = c('readlength'))
dorado_readslength4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/readlength.dorado.txt"), col.names = c('readlength'))
dorado_readslength5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/readlength.dorado.txt"), col.names = c('readlength'))
dorado_readslength6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/readlength.dorado.txt"), col.names = c('readlength'))
dorado_readslength7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/readlength.dorado.txt"), col.names = c('readlength'))
dorado_readslength8<- fread(paste0(datapath, "/12_Cases_Tconv-7/readlength.dorado.txt"), col.names = c('readlength'))


#sets read ID-Column to Name of data set
dorado_readslength1$sample<-"Cases-Treg-5"
dorado_readslength2$sample<-"Cases-HD3-Treg-3"
dorado_readslength3$sample<-"Cases-HD3-Treg-6"
dorado_readslength4$sample<-"20211208_HD42_Lib1_dRNA002"
dorado_readslength5$sample<-"20211209_HD42_Lib1_RNA002"
dorado_readslength6$sample<-"20220105_HD43_dRNA_RNA002"
dorado_readslength7$sample<-"Cases-Treg-HD2"
dorado_readslength8$sample<-"Cases_Tconv-7"

#combine files to one 
whole_dorado_readslength <- rbind(dorado_readslength1,dorado_readslength2,dorado_readslength3,dorado_readslength4,dorado_readslength5,dorado_readslength6,dorado_readslength7,dorado_readslength8)
   #removes unused data, to save RAM capacity
    rm(dorado_readslength1,dorado_readslength2,dorado_readslength3,dorado_readslength4,dorado_readslength5,dorado_readslength6,dorado_readslength7,dorado_readslength8)


#creates violin plots
dorado_readslength_v <- ggplot(whole_dorado_readslength, 
                  aes(x=sample, y=readlength)) + 
                  geom_violin(scale = "width")  + 
                  geom_boxplot(width=0.03,  outlier.shape = NA) + 
                  labs(x = NULL)+
                  scale_y_continuous(limits = c(0, 5000)) +
                  ggtitle ("Length of all aligning reads after basecalling") + 
                  theme_classic() +
                  theme(axis.text.x = element_text(angle = 45, hjust = 1))

``` 

#Read length distribution 
#all reads aligning to HG38
```{r} 
#reads files and creates a dataframe
HG38_readslength1<- fread(paste0(datapath, "/13_Cases-Treg-5/readlength.nonENO2.aligning.txt"), col.names = c('readlength'))
HG38_readslength2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/readlength.nonENO2.aligning.txt"), col.names = c('readlength'))
HG38_readslength3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/readlength.nonENO2.aligning.txt"), col.names = c('readlength'))
HG38_readslength4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/readlength.nonENO2.aligning.txt"), col.names = c('readlength'))
HG38_readslength5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/readlength.nonENO2.aligning.txt"), col.names = c('readlength'))
HG38_readslength6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/readlength.nonENO2.aligning.txt"), col.names = c('readlength'))
HG38_readslength7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/readlength.nonENO2.aligning.txt"), col.names = c('readlength'))
HG38_readslength8<- fread(paste0(datapath, "/12_Cases_Tconv-7/readlength.nonENO2.aligning.txt"), col.names = c('readlength'))


#sets read ID-Column to Name of data set
HG38_readslength1$sample<-"Cases-Treg-5"
HG38_readslength2$sample<-"Cases-HD3-Treg-3"
HG38_readslength3$sample<-"Cases-HD3-Treg-6"
HG38_readslength4$sample<-"20211208_HD42_Lib1_dRNA002"
HG38_readslength5$sample<-"20211209_HD42_Lib1_RNA002"
HG38_readslength6$sample<-"20220105_HD43_dRNA_RNA002"
HG38_readslength7$sample<-"Cases-Treg-HD2"
HG38_readslength8$sample<-"Cases_Tconv-7"

#combine files to one 
whole_HG38_readslength <- rbind(HG38_readslength1,HG38_readslength2,HG38_readslength3,HG38_readslength4,HG38_readslength5,HG38_readslength6,HG38_readslength7,HG38_readslength8)
  #removes unused data, to save RAM capacity
    rm(HG38_readslength1,HG38_readslength2,HG38_readslength3,HG38_readslength4,HG38_readslength5,HG38_readslength6,HG38_readslength7,HG38_readslength8)


#creates violin plots
HG38_readslength_v <- ggplot(whole_HG38_readslength, 
                  aes(x=sample, y=readlength)) + 
                  geom_violin(scale = "width")  + 
                  geom_boxplot(width=0.03,  outlier.shape = NA) + 
                  labs(x = NULL)+
                  scale_y_continuous(limits = c(0, 5000)) +
                  ggtitle ("Length of all reads aligning to just HG38") + 
                  theme_classic() +
                  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#(HG38_readslength_v)
``` 

#Read length distribution 
#reads not aligning to HG38 or ENO2
```{r} 
#reads files and creates a dataframe
nonalign_readslength1<- fread(paste0(datapath, "/13_Cases-Treg-5/readlength.nonaligning.txt"), col.names = c('readlength'))
nonalign_readslength2<- fread(paste0(datapath, "/01_Cases-HD3-Treg-3/readlength.nonaligning.txt"), col.names = c('readlength'))
nonalign_readslength3<- fread(paste0(datapath, "/02_Cases-HD3-Treg-6/readlength.nonaligning.txt"), col.names = c('readlength'))
nonalign_readslength4<- fread(paste0(datapath, "/03_20211208_HD42_Lib1_dRNA002/readlength.nonaligning.txt"), col.names = c('readlength'))
nonalign_readslength5<- fread(paste0(datapath, "/04_20211209_HD42_Lib1_RNA002/readlength.nonaligning.txt"), col.names = c('readlength'))
nonalign_readslength6<- fread(paste0(datapath, "/05_20220105_HD43_dRNA_RNA002/readlength.nonaligning.txt"), col.names = c('readlength'))
nonalign_readslength7<- fread(paste0(datapath, "/08_Cases-Treg-HD2/readlength.nonaligning.txt"), col.names = c('readlength'))
nonalign_readslength8<- fread(paste0(datapath, "/12_Cases_Tconv-7/readlength.nonaligning.txt"), col.names = c('readlength'))


#sets read ID-Column to Name of data set
nonalign_readslength1$sample<-"Cases-Treg-5"
nonalign_readslength2$sample<-"Cases-HD3-Treg-3"
nonalign_readslength3$sample<-"Cases-HD3-Treg-6"
nonalign_readslength4$sample<-"20211208_HD42_Lib1_dRNA002"
nonalign_readslength5$sample<-"20211209_HD42_Lib1_RNA002"
nonalign_readslength6$sample<-"20220105_HD43_dRNA_RNA002"
nonalign_readslength7$sample<-"Cases-Treg-HD2"
nonalign_readslength8$sample<-"Cases_Tconv-7"

#combine files to one 
whole_nonalign_readslength <- rbind(nonalign_readslength1,nonalign_readslength2,nonalign_readslength3,nonalign_readslength4,nonalign_readslength5,nonalign_readslength6,nonalign_readslength7,nonalign_readslength8)

  #removes unused data, to save RAM capacity
    rm(nonalign_readslength1,nonalign_readslength2,nonalign_readslength3,nonalign_readslength4,nonalign_readslength5,nonalign_readslength6,nonalign_readslength7,nonalign_readslength8)


#creates violin plots
nonalign_readslength_v <- ggplot(whole_nonalign_readslength, 
                  aes(x=sample, y=readlength)) + 
                  geom_violin(scale = "width")  + 
                  geom_boxplot(width=0.03,  outlier.shape = NA) + 
                  labs(x = NULL)+
                  scale_y_continuous(limits = c(0, 5000)) +
                  ggtitle ("Length of all nonaligning reads") + 
                  theme_classic() +
                  theme(axis.text.x = element_text(angle = 45, hjust = 1))
#(nonalign_readslength_v)
``` 

##Plot Creation of read length overview
```{r} 
(all_readslength_v | dorado_readslength_v)/
  (HG38_readslength_v | nonalign_readslength_v)
``` 

##Final Plot
```{r} 
pdf(file="sample Overview.pdf", width =24, height = 20) 
  (FOXP3_v | whole_v | whole_zoom_v ) /
(FOXP3_counts | whole_counts| readcomposition_bp)/
(all_readslength_v | dorado_readslength_v)/
(HG38_readslength_v | nonalign_readslength_v)
dev.off()

pdf(file="Poly(A) length Overview.pdf", width =24, height = 20) 
  (FOXP3_v | whole_v | whole_zoom_v ) /
(FOXP3_counts | whole_counts)
dev.off()

pdf(file="read length Overview.pdf", width =24, height = 20) 
 (all_readslength_v | dorado_readslength_v |readcomposition_bp)/
(HG38_readslength_v | nonalign_readslength_v)
dev.off()


``` 